\documentclass[10pt]{beamer}

\usetheme{metropolis}           % Use metropolis theme

\usepackage{minted}

\author{Austin Jones}
\title{DigitStringDiv1 \-- SRM 741, D1, 250-Pointer}
\date{\today}

\institute{University of Tennessee \-- Knoxville}

\begin{document}

\maketitle

\section{Problem Intro}

\begin{frame}[fragile]{Statement and Constraints}
  \begin{minted}{cpp}
    class DigitStringDiv1 {
      public:
        long long count(string s, int x);
    };
  \end{minted}
  \begin{itemize}
    \item Given: S, string containing characters from '0' through '9' and is at most 47 characters in length.
    \item Given: X, integer between 0 and 777,444,111.
    \item A subsequence of S is a string that results when you erase some subset of indices of S.
    \item e.g. S is ``12356'', ``13'' and ``256'' are subsequences. ``61'' is not.
    \item Count the number of subsequences of S that are greater than X.
  \end{itemize}
\end{frame}

\begin{frame}{Example}
  EXAMPLE HERE
\end{frame}

\section{Slow, Dumb Way}

\begin{frame}{First Frame}
  Hello, world!
\end{frame}

\section{Fast, Smart Way}

\begin{frame}{First Frame}
  Hello, world!
\end{frame}


\section{Wrapping Up}

\begin{frame}{How did Topcoder Do?}
  \begin{itemize}
    \item Problem Given in Topcoder: November, 2018
    \item Competitors who opened the problem: 99
    \item Competitors who submitted a solution: 82
    \item Number of correct solutions: 42
    \item Accuracy (percentage correct vs those who opened): 49.4%
    \item Average Correct Time: 24.59
    \item Best Time: 4:56
  \end{itemize}
\end{frame}

\begin{frame}{Thank You}
  \Huge Questions?
\end{frame}

\end{document}

